Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-21 Markdown Documents/Manuscript.Rmd
added a sick dumbbell fig

We can apply these visitation estimates to the fee data/predictions also. This gives us the following table.
```{r echo=FALSE, cache=TRUE}
fitint<-as.data.frame(posterior_interval(fit))
names(fitint)<-c("CI5","CI95")
fitint$Par<-row.names(fitint)
fitsig<-fitint[grep("stdsmoke UnitCode",row.names(fitint)),]%>% 
  filter(CI5<0 & CI95<0)

@@

summaryFinancialLoss<-summaryFinancialLoss[,c(6,4,5)]
summaryFinancialLoss$IncomeDif<-currency(summaryFinancialLoss$IncomeDif)
names(summaryFinancialLoss)<-(c("National Park","Income Loss Estimate (1980-2018)", "Percent Income Loss (1980-2018)"))
summaryFinancialLoss$`Percent Income Loss (1980-2018)`<-paste0(summaryFinancialLoss$`Percent Income Loss (1980-2018)`,'%')
formattable::formattable(summaryFinancialLoss)
```
## 3.3. Model Validation
To assess the validity of our model, we used a k-fold cross validation technique.

>>>>

```{r echo=FALSE, cache=TRUE}
fitint<-as.data.frame(posterior_interval(fit))
names(fitint)<-c("CI5","CI95")
fitint$Par<-row.names(fitint)
fitsig<-fitint[grep("stdsmoke UnitCode",row.names(fitint)),]%>% 
  filter(CI5<0 & CI95<0)

@@

summaryFinancialLoss<-summaryFinancialLoss[,c(6,4,5)]
summaryFinancialLoss$IncomeDif<-currency(summaryFinancialLoss$IncomeDif)
names(summaryFinancialLoss)<-(c("National Park","Income Loss Estimate (1980-2018)", "Percent Income Loss (1980-2018)"))
summaryFinancialLoss$`Percent Income Loss (1980-2018)`<-paste0(summaryFinancialLoss$`Percent Income Loss (1980-2018)`,'%')
```

```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 12}
dat%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(totrec=sum(RecreationVisits),totpred=sum(PredNoSmoke50CI))%>%ungroup()%>%
  mutate(diff=totpred-totrec)%>%
ggplot(., 
       aes(y = reorder(ParkName,diff),
           x = totrec,
           xend = totpred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#1f78b4",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey") +
  scale_x_continuous( breaks=seq(10000000,90000000,20000000),labels = scales::comma) + 
  labs(title = "Total Lost Visitation",
       subtitle = "1980 to 2018",
       x = "Total Visits",
       y = "")+theme_classic()+mytheme

We can apply these visitation estimates to the fee data/predictions also. This gives us the following table.
```{r echo=FALSE, cache=TRUE}

formattable::formattable(summaryFinancialLoss)
```

## 3.3. Model Validation
To assess the validity of our model, we used a k-fold cross validation technique.
